Forecasting interrupted time series

### 2023-07-28 fits.qmd
Added ABS ref
Adjustments to tourism examples

The Australian tourism data set is a monthly time series showing the number of short-term overseas visitors to Australia. The data are available from January 2000 to May 2023, and are shown in @fig-tourism_plot1. As the borders closed in March 2020, the number of visitors to Australia dropped to near zero, and remained there until towards the end of 2021. The borders officially reopened on 21 February 2022, although it seems visitors began to arrive earlier than that. The data are available from the Australian Bureau of Statistics.

```{r}
#| label: fig-tourism_plot1
#| caption: Australian tourism data"
#| fig-height: 3
tar_read(tourism_plot1)
```

@@

```{r}
#| label: fig-tsol1_plot
#| fig-height: 8
#| fig-caption: Solution 1. ETS is highly adaptive.
tar_read(tsol1_plot)
```

```{r}
#| label: fig-tsol2_plot
#| fig-height: 8
#| fig-caption: Solution 2. We use a left shift in March 2020, and a ramp from November 2022.
tar_read(tsol2_plot)
```

```{r}
#| label: fig-tsol3_plot
#| fig-height: 8
#| fig-caption: Solution 3. The period from March 2020 to November 2022 is set to missing.
tar_read(tsol3_plot)
```

```{r}
#| label: fig-tsol4_plot
#| fig-height: 8
#| fig-caption: Solution 4. The period from March 2020 to November 2022 is set to missing.
tar_read(tsol4_plot)
```

>>>>

The Australian tourism data set is a monthly time series showing the number of short-term overseas visitors to Australia. The data [@tourismdata] are available from January 2000 to May 2023, and are shown in @fig-tourism_plot1. As the borders closed in March 2020, the number of visitors to Australia dropped to near zero, and remained there until towards the end of 2021. The borders officially reopened on 21 February 2022, although it seems visitors began to arrive earlier than that. The data are available from the Australian Bureau of Statistics.

```{r}
#| label: fig-tourism_plot1
#| fig-cap: "Short-term visitor arrivals to Australia (monthly): Jan 2000 -- May 2023."
#| fig-height: 3
tar_read(tourism_plot1)
```

@@

```{r}
#| label: fig-tsol1_plot
#| fig-height: 8
#| fig-cap: Solution 1. This should show that ETS is highly adaptive. However, for some reason, that is no longer the case, and I don't know why.
tar_read(tsol1_plot)
```

```{r}
#| label: fig-tsol2_plot
#| fig-height: 8
#| fig-cap: Solution 2. We use a left shift in March 2020, and a ramp from November 2022 to June 2023.
tar_read(tsol2_plot)
```

```{r}
#| label: fig-tsol3_plot
#| fig-height: 8
#| fig-cap: Solution 3. The period from March 2020 to November 2022 is set to missing. So the first three years of forecasts show what might have been. The fourth set of forecasts uses observations from November and December 2022, and so the forecasts have been adjusted downwards.
tar_read(tsol3_plot)
```

```{r}
#| label: fig-tsol4_plot
#| fig-height: 8
#| fig-cap: Solution 4. We replace the observations from March 2020 to November 2022 with the average of the same month in the 3 preceding years. 
tar_read(tsol4_plot)
```

### 2023-07-28 fits.tex
Adjustments to tourism examples

\usepackage[section]{placeins}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners, frame hidden, enhanced]}{\end{tcolorbox}}\fi
\makeatother
\makeatletter
\makeatother

@@

The Australian tourism data set is a monthly time series showing the
number of short-term overseas visitors to Australia. The data are
available from January 2000 to May 2023, and are shown in
Figure~\ref{fig-tourism_plot1}. As the borders closed in March 2020, the
number of visitors to Australia dropped to near zero, and remained there
until towards the end of 2021. The borders officially reopened on 21
February 2022, although it seems visitors began to arrive earlier than
that. The data are available from the Australian Bureau of Statistics.

@@

\caption{\label{fig-tourism_plot1}\textbf{?(caption)}}

@@

\caption{\label{fig-tsol1_plot}\textbf{?(caption)}}

@@

\caption{\label{fig-tsol2_plot}\textbf{?(caption)}}

@@

\caption{\label{fig-tsol3_plot}\textbf{?(caption)}}

@@

\caption{\label{fig-tsol4_plot}\textbf{?(caption)}}

>>>>

\usepackage[section]{placeins}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, breakable, frame hidden, interior hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
\makeatother
\makeatletter
\makeatother

@@

The Australian tourism data set is a monthly time series showing the
number of short-term overseas visitors to Australia. The data
\autocite{tourismdata} are available from January 2000 to May 2023, and
are shown in Figure~\ref{fig-tourism_plot1}. As the borders closed in
March 2020, the number of visitors to Australia dropped to near zero,
and remained there until towards the end of 2021. The borders officially
reopened on 21 February 2022, although it seems visitors began to arrive
earlier than that. The data are available from the Australian Bureau of
Statistics.

@@

\caption{\label{fig-tourism_plot1}Short-term visitor arrivals to
Australia (monthly): Jan 2000 -- May 2023.}

@@

\caption{\label{fig-tsol1_plot}Solution 1. This should show that ETS is
highly adaptive. However, for some reason, that is no longer the case,
and I don't know why.}

@@

\caption{\label{fig-tsol2_plot}Solution 2. We use a left shift in March
2020, and a ramp from November 2022. We possibly need to stop the ramp
around mid 2023.}

@@

\caption{\label{fig-tsol3_plot}Solution 3. The period from March 2020 to
November 2022 is set to missing. So the first three years of forecasts
show what might have been. The fourth set of forecasts uses observations
from November and December 2022, and so the forecasts have been adjusted
downwards.}

@@

\caption{\label{fig-tsol4_plot}Solution 4. We replace the observations
from March 2020 to November 2022 with the average of the same month in
the 3 preceding years.}
